---
title: "Auto Insurance Fraud Detection"
author: "Raikibul HASAN"
date: "2023-01-03"
output:
  html_document: default
  pdf_document: default
---

\newunicodechar{₁}{\ensuremath{{}_1}}

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE,message=FALSE)  
```

**Use "renv::restore()" then "renv::activate()" to install all of the library and dependencies".**

# Contents

**Click on link for quick view:**

0.  [Load Libraries](#load)
1.  [Data pre-processing](#pre_pro)

-   1.1 Load data set

-   1.2 Data Understanding

    -   statistics view

-   1.3 Data cleaning & Handling Missing value

    -   finding missing values\
    -   inconsistencies among variable\
    -   replace missing values\
    -   fixing incorrect data points\

-   1.4 Exploratory Data Analysis

    -   Uni variate Analysis
        -   Numerical Variables\
        -   Categorical Variables\
    -   Multivariate Analysis\

-   1.5 Feature Selection & Feature Engineering

    -   fixing outliers\
    -   Encoding\
    -   find features relevant to the model

-   1.6 Train- Test split

-   split data 80% for training & 20% for testing\

2.  [MACHINE LEARNING MODEL](#model)

-   2.1 Support Vector Classifier
-   2.2 Decision Tree Classifier
-   2.3 Random Forest Classifier
-   2.4 Logistic regression
-   2.5 Hyper parameter Tuning - Random Search - Grid Search
-   2.6 Prediction With balance data

3.  [Models Comparison](#comparison)

-   3.1 Accuracy comparison
-   3.2 F1 , Precision & Recall score Comparison

# 0 Load Libraries <a name="load"></a>

```{r}
library(ggplot2)
library(readr)
library(visdat)
library(tidyverse)
library(caret)
library(magrittr)
library(Metrics)
library(precrec)
library(ROSE) 
library(randomForest)
library(rpart)
library(rpart.plot)
library(ggcorrplot)
library(dplyr)
library(pROC)
library(data.table)
library(mltools)
library(psych)
library(cvms)
library(kernlab)
library(ROSE)
```

# 1. Data Pre-processing <a name="pre_pro"></a>

## 1.1 Load data set

```{r}
insurance_claims <- read_csv("data/insurance_claims.csv")
insurance_claims
```

## 1.2 Data Understanding

```{r}
cat("Number of rows and columns", dim(insurance_claims))
head(insurance_claims)
```

Let's have a statistics overview of our data set.

```{r}
summary(insurance_claims)
```

We want to see the type of every feature in our data set.

```{r}
str(insurance_claims)
```

## 1.3 Data cleaning & Handling Missing values

```{r}
drop <- c("incident_date","policy_bind_date")
df_1 = insurance_claims[,!(names(insurance_claims) %in% drop)]
df_1
```

We have some missing values denoted by "?" So, we first replace those with "NA"

```{r}
df_1[df_1=="?"] <- NA
vis_miss(df_1,)
```

```{r}
colSums(is.na(df_1))
```

As The column "\_c39" doesn't have any data,lets remove this column.

```{r}
cat("Before : ",dim(df_1))
df_1 = df_1[,!(names(df_1) %in% c("_c39"))]
cat("\nAfter : ",dim(df_1))
```

For column collision_type,property_damage,police_report_available, fill the missing value with mode.

```{r}
fill_missing_value <- function(df,col_name) {
  mode=names(which.max(table(df$col_name)))
  df$col_name[is.na(df$col_name)] <- mode
}
df_1$collision_type<-fill_missing_value(df_1,collision_type)
df_1$property_damage<-fill_missing_value(df_1,property_damage)
df_1$police_report_available<-fill_missing_value(df_1,police_report_available)
vis_miss(df_1,cluster = TRUE)
```

## 1.4 Exploratory Data Analysis

```{r}
df_2=df_1
describe(df_2)
```

Let's filter the Categorical column from df_2

```{r}
categorical<- df_2 %>% select_if(negate(is.numeric))
categorical
```

We don't add to much visualization for this part ,as we have a lot of columns. We just visualize one/two plot here.

```{r}
categorical %>% summarise_all(funs(n_distinct(.)))
```

#### Uni-variate Analysis

```{r}
g <- ggplot(df_2, aes(fraud_reported,fill=fraud_reported))
g + geom_bar( )
df_2 %>% 
  count(fraud_reported)
```

```{r}
g <- ggplot(df_2, aes(insured_hobbies,fill=insured_hobbies))
g + geom_bar( )
```

```{r}
g <- ggplot(df_2, aes(incident_severity,fill=incident_severity))
g + geom_bar()
```

```{r}
g <- ggplot(df_2, aes(incident_type,fill=incident_type))
g + geom_bar()

```

```{r}
numeric<- df_2 %>% select(where(is.numeric))
numeric
```

```{r}
df_2%>%
  ggplot(aes(age))+
  geom_histogram(binwidth = 2, fill = "#0C8E7A")+
  theme_bw()+
  labs(title="Age")
```

```{r}
ggplot(stack(numeric[,1:5]), aes(x = ind, y = values,fill="#0C8E7A")) +
  geom_boxplot()
```

```{r}
ggplot(stack(numeric[,6:10]), aes(x = ind, y = values,fill="#0C8E7A")) +
  geom_boxplot()

```

```{r}
ggplot(stack(numeric[,11:15]), aes(x = ind, y = values,fill="#0C8E7A")) +
  geom_boxplot()

```

```{r}
ggplot(stack(numeric[,16:18]), aes(x = ind, y = values,fill="#0C8E7A")) +
  geom_boxplot()

```

```{r}
outliers <- function(x) {

  Q1 <- quantile(x, probs=.25)
  Q3 <- quantile(x, probs=.75)
  iqr = Q3-Q1

 upper_limit = Q3 + (iqr*1.5)
 lower_limit = Q1 - (iqr*1.5)

 x > upper_limit | x < lower_limit
}

remove_outliers <- function(df, cols = names(df)) {
  for (col in cols) {
    df <- df[!outliers(df[[col]]),]
  }
  df
}
remove_outliers(df_2, c('total_claim_amount', 'umbrella_limit', 'property_claim'))
```

### Multivariate Analysis

```{r}
df_2 %>%
ggplot(aes(x =policy_annual_premium ,
fill = insured_sex,
color = insured_sex)) +
geom_density(alpha = 0.7)+
  labs(x= "policy_annual_premium" ,
     title="policy_annual_premium based  on sex")+
theme(plot.caption = element_text(face = "italic"))
```

```{r}
df_2 <- df_1 %>% 
  mutate(fraud_reported = recode(fraud_reported, 
                    "Y" = 1, 
                    "N" = 0))
str(df_2$fraud_reported)
```

```{r fig.height=8,fig.width=8}
model.matrix(~0+., data=numeric) %>% 
  cor(use="pairwise.complete.obs") %>% 
  ggcorrplot(lab=TRUE, lab_size=3,sig.level = 0.05,tl.cex = 12)
```

## 1.5 Feature Engineering

```{r}
irrelevent_col = c('policy_number','policy_bind_date','policy_state','insured_zip','incident_location','incident_date','incident_state','incident_city','insured_hobbies','auto_make','auto_model','auto_year')
model_df = df_2[,!(names(df_2) %in% irrelevent_col)]
model_df


```

```{r}
model_df = model_df %>% mutate_if(is.character,as.factor) 
model_df = as.data.frame(model_df)
model_df <- one_hot(as.data.table(model_df))
```

```{r}
corr <- cor(model_df)
corr_fraud <- as.data.frame(corr[,61])
names(corr_fraud) <- c("fraud_reported")
sorted_feat <- corr_fraud %>% arrange(desc(abs(fraud_reported)))
top_corr<- sorted_feat %>% 
              filter(abs(fraud_reported)>0.1 & abs(fraud_reported) != 1) 
top_corr
```

```{r}
head(model_df)
```

## 1.6 Train- Test split

```{r}
train = data.frame(model_df)
train_index = createDataPartition(train$fraud_reported, times = 1, p=0.8, list=F)
train_data = train[train_index,]
test_data = train[-train_index,]
dim(train_data)
dim(test_data)
```

# 2 MACHINE LEARNING MODEL <a name="model"></a>

### 2.1 Support Vector Classifier

```{r}
svm <- ksvm(as.factor(fraud_reported) ~ . , data= train_data, kernel='rbfdot', )
print(svm)
pred_svm <- predict(svm, test_data)
cf_svm<-confusionMatrix(pred_svm,as.factor(test_data$fraud_reported),mode = "everything",dnn=c("Prediction","Reference"))
performance <- pred_svm == test_data$fraud_reported
table(performance)
prop.table(table(performance))
cf_svm
```

```{r}
table <- data.frame(cf_svm$table)

plot_confusion_matrix(table, 
                      target_col = "Reference", 
                      prediction_col = "Prediction",
                      counts_col = "Freq")
```

## 2.2 Decision Tree Classifier

```{r }
decision_tree_model <- rpart(as.factor(fraud_reported)~., data=train_data)
rpart.plot(decision_tree_model)
```

```{r}
prediction_dt <- predict(decision_tree_model,test_data,type = 'class')
CFM_dt<-confusionMatrix(prediction_dt,as.factor(test_data$fraud_reported),mode = "everything",dnn=c("Prediction","Reference"))
CFM_dt
```

```{r}
table <- data.frame(CFM_dt$table)

plot_confusion_matrix(table, 
                      target_col = "Reference", 
                      prediction_col = "Prediction",
                      counts_col = "Freq")

```

## 2.3 Logistic regression

```{r}
log_reg_model <- glm(fraud_reported~., data=train_data, family=binomial)
# Compute the predictions
proba_logreg <- predict(log_reg_model, test_data, type="response")
pred_logreg <- ifelse(proba_logreg<0.5, 0, 1)
pred_logreg <- factor(pred_logreg)
# Store the confusion matrix and other metrics
CFM_log_reg<-confusionMatrix(pred_logreg,as.factor(test_data$fraud_reported),mode = "everything",dnn=c("Prediction","Reference"))
table <- data.frame(CFM_log_reg$table)
CFM_log_reg
```

```{r}
plot_confusion_matrix(table, 
                      target_col = "Reference", 
                      prediction_col = "Prediction",
                      counts_col = "Freq")
```

## 2.4 Random Forest Classifier

```{r}
random_forest <- randomForest(as.factor(fraud_reported)~., data=train_data, proximity=TRUE,importance=TRUE)
varImpPlot(random_forest,type=2,pch=15,col=1,cex=1,main="IMPORTANCE(varImpPlot)")
```

```{r}
hist(treesize(random_forest))

```

```{r}
# Compute the predictions
prediction_rf <- predict(random_forest, test_data)
cf_rf<-confusionMatrix(prediction_rf,as.factor(test_data$fraud_reported),mode = "everything",dnn=c("Prediction","Reference"))
cf_rf
```

```{r}
table <- data.frame(cf_rf$table)
plot_confusion_matrix(table, 
                      target_col = "Reference", 
                      prediction_col = "Prediction",
                      counts_col = "Freq")
```

Plot roc curve for Random_forest Classifier

```{r}
ran_roc <- roc(as.factor(test_data$fraud_reported),as.numeric(prediction_rf))
plot(ran_roc, print.auc=TRUE, auc.polygon=TRUE, grid=c(0.1, 0.2),grid.col=c("green", "red"), max.auc.polygon=TRUE,auc.polygon.col="skyblue", print.thres=TRUE,main='ROC curve of random forest model, Mtry =6,ntree=500')

#set model in evaluation mood
prediction_rf = evalmod(scores = as.numeric(prediction_rf), labels = test_data$fraud_reported, mode = "rocprc")
prediction_rf
```

## 2.5 Hyper parameter Tuning

### Random search

```{r}
#10 folds repeat 3 times
control <- trainControl(method='repeatedcv', 
                        number=10, 
                        repeats=3,
                        search = 'random')


rf_random <- train(as.factor(fraud_reported) ~ .,
                   data = model_df,
                   method = 'rf',
                   metric = 'Accuracy',
                 tuneLength  = 15, 
                   trControl = control)
print(rf_random)
```

```{r}
plot(rf_random)
```

### Grid Search

```{r}
control <- trainControl(method='repeatedcv', 
                        number=10, 
                        repeats=3, 
                        search='grid')

tunegrid <- expand.grid(.mtry = (1:15)) 

rf_gridsearch <- train(as.factor(fraud_reported) ~ ., 
                       data = model_df,
                       method = 'rf',
                       metric = 'Accuracy',
                       tuneGrid = tunegrid)
print(rf_gridsearch)
plot(rf_gridsearch)
```

### 2.6 Lets check by blancing data wheather Accuracy increase?

Check the best model with balance data set . For this purpose , we use both sampling method at the same time.

```{r}
balanced_data <- ovun.sample(as.factor(fraud_reported) ~ ., data = train_data, method = "both", p=0.5,N=800, seed = 1)$data
```

-   Try with Support Vector Classifier with the balance data.

```{r}
svm <- ksvm(as.factor(fraud_reported) ~ . , data= balanced_data, kernel='rbfdot', )
print(svm)
pred_svm <- predict(svm, test_data)
cf_svm_samp<-confusionMatrix(pred_svm,as.factor(test_data$fraud_reported),mode = "everything",dnn=c("Prediction","Reference"))
performance <- pred_svm == test_data$fraud_reported
table(performance)
prop.table(table(performance))
cf_svm_samp
```

# 3 Model Comparison <a name="comparison"></a>

## 3.1 Accuracy Comparison Table

```{r}
accuracy_svm <- cf_svm$overall['Accuracy']*100
accuracy_dt <- CFM_dt$overall['Accuracy']*100
accuracy_log <- CFM_log_reg$overall['Accuracy']*100
accuracy_RF <- cf_rf$overall['Accuracy']*100
accuracy_svm_sampling <- cf_svm_samp$overall['Accuracy']*100

Model_name <- c("SVC","Decission_tree","Logistic_regression","Random_forest",
            "SVC_Balanced")
accuracy<-c( accuracy_svm,accuracy_dt,accuracy_log,accuracy_RF,
            accuracy_svm_sampling)
model_accuracy_com<- data.frame(Model_name,accuracy)
model_accuracy_com
```

```{r}
ggplot(model_accuracy_com, aes(Model_name, accuracy, fill = Model_name)) +
  geom_bar(stat="identity", position = "dodge") +
  labs(title="Model Accuracy Comparison")
```

## 3.2 F1, Precision & Recall Score Comparison

```{r}
f1_svm <- cf_svm$byClass['F1']*100 
pre_svm <- cf_svm$byClass['Precision']*100 
re_svm <- cf_svm$byClass['Recall']*100 

f1_dt <- CFM_dt$byClass['F1']*100 
pre_dt <- CFM_dt$byClass['Precision']*100 
re_dt <- CFM_dt$byClass['Recall']*100 

f1_log <- cf_svm$byClass['F1']*100 
pre_log <- cf_svm$byClass['Precision']*100 
re_log <- cf_svm$byClass['Recall']*100 

f1_RF <- cf_rf$byClass['F1']*100 
pre_RF <- cf_rf$byClass['Precision']*100 
re_RF <- cf_rf$byClass['Recall']*100 

f1_svm_samp <- cf_svm_samp$byClass['F1']*100 
pre_svm_samp <- cf_svm_samp$byClass['Precision']*100 
re_svm_samp <- cf_svm_samp$byClass['Recall']*100 

f1_score<-c( f1_svm,f1_dt,f1_log,f1_RF,f1_svm_samp)

precison_score<-c( pre_svm,pre_dt,pre_log,pre_RF,pre_svm_samp)

recall_score<-c( re_svm,re_dt,re_log,re_RF,re_svm_samp)
model_com_fpr<- data.frame(Model_name,f1_score,precison_score,recall_score)
model_com_fpr
```

```{r}
top_corr
```

```{r}
train = data.frame(model_df)
train_index = createDataPartition(train$fraud_reported, times = 1, p=0.8, list=F)
train_data = train[train_index,]
test_data = train[-train_index,]
dim(train_data)
dim(test_data)

```

Lets check one more time, our top correlated column with target variable from feature selection part(1.5). Check weather the accuracy increase or not!

```{r}
top_corlist <- c("incident_severity_Major.Damage","incident_severity_Minor.Damage", "incident_severity_Total.Loss","vehicle_claim","total_claim_amount", "property_claim","authorities_contacted_None","incident_severity_Trivial.Damage","incident_type_Vehicle.Theft","incident_type_Parked.Car","fraud_reported")
traindata_with_top_f<-subset(train_data,select= top_corlist)
```

```{r}

svm_mod <- ksvm(as.factor(fraud_reported) ~ . , data= traindata_with_top_f, kernel='rbfdot', )
pred_svm_mod <- predict(svm_mod, test_data)
cf_svm_samp<-confusionMatrix(pred_svm_mod,as.factor(test_data$fraud_reported),mode = "everything",dnn=c("Prediction","Reference"))

cf_svm_samp
```

We see from this workshop, the difficulty with detecting fraud using machine learning is that fraudulent claims are much less frequent than legitimate ones(Imbalanced data set).And another problem is that this data set has limited sample size.

**THANK YOU**\
**HAPPY CODING :)**
